Free Probability Analysis of Capacity in Relay Networks

### 2020-04-09 documentation/systemModel/systemModel.tex
recursion and secrecy capacity fixed

Using the model from the decontamination work we say the total channel is described by 
\begin{equation}
\mathbf{D} = \sum_{k=1}^{K}\mathbf{D}_k = \sum_{k=1}^{K} \alpha_k \mathbf{B}_k \mathbf{C}_k
\end{equation}
We now consider how to ultimately arrive at an expression for the AED of $DD^H$
\begin{itemize}

\item 
	We first find the Stieltjes transform of each term in the total channel $G_{D_kD_k^H}(s)$.
\item
	Now we use a key property of the Stieljes transform
	\begin{equation}
	G_{\lambda^2}(s) = \frac{G_{\lambda}(\sqrt{s})- G_{\lambda}(-\sqrt{s})}{2\sqrt{s}}
	\end{equation}
	to find the Stieltjes transform of the symmetrized singular value decomposition of $D_k$.
\item
	Taking the R-transform, $\tilde{R}_{D_k}(w)$ of the result, we then use the free additive convolution property in order to 
	find the R-transform of the entire equivalent channel $\tilde{R}_{D}(w)$. 
\item
	Using the key property of the Stieltjes transform again we can find the the R-transform of the 
	covariance matrix of the symmetrized channel, $\tilde{R}_{DD^H}(w)$ . We can then find $\tilde{G}_{DD^H}(s)$ and 
	use the inversion to find the symmetrized AED.

@@

\subsection{Solving for $G_{D_kD_k^H}(s)$ } 
For the model presented we have 
\begin{equation}
D_k = G_B \boldsymbol{\Theta}_N H_N \cdots \boldsymbol{\Theta}_1 H_1
\end{equation}
and 
\begin{equation}
C_N = D_kD_k^H = [G_B \boldsymbol{\Theta}_N H_N \cdots \boldsymbol{\Theta}_1 H_1]
[H_1 \boldsymbol{\Theta}_1 \cdots H_N \boldsymbol{\Theta}_N G_B]
\end{equation}
\begin{itemize}
\item 
	Because commuting matrix multiplication does not change the non-zero eigen value distribution, we consider 
	the matrix 
\begin{equation}
\tilde{C}_N = [\boldsymbol{\Theta}_1^H \cdots H_N^H \boldsymbol{\Theta}_N^H G_B^H][G_B \boldsymbol{\Theta}_N  \cdots \boldsymbol{\Theta}_1 H_1 H_1^H]
\end{equation}

\item 
	We use the following key property of the Stieltjes transform and S-Transform. 
\begin{equation}
S_{C_N}(z) = \frac{z+1}{z+\chi_N} S_{\tilde{C}_N}(\frac{z}{\chi_N})
\end{equation}

>>>>

Using the model from the decontamination work we say the total channel is described by 
\begin{equation}
\mathbf{D} = \sum_{k=1}^{K}\mathbf{D}_k 
\end{equation}
We now consider how to ultimately arrive at an expression for the AED of $DD^H$
\begin{itemize}

\item 
	We first find the Stieltjes transform, $G_{D_kD_k^H}(s)$, for the AED of each term, $D_k$.
	This is discussed further in Section \ref{Polynomial_terms}.
\item
	Now we use a property of the Stieljes transform
	\begin{equation}\label{ST_property}
	G_{\lambda^2}(s) = \frac{G_{\lambda}(\sqrt{s})- G_{\lambda}(-\sqrt{s})}{2\sqrt{s}}
	\end{equation}
	to find the Stieltjes transform of the symmetrized singular value decomposition of
	 $D_k$, $\tilde{G}_{D_k}(s)$. Note that is property is reasonable to use because
	 we consider Gaussian  $D_k$ which are bi-unitarily invariant.
\item
	Taking the R-transform, $\tilde{R}_{D_k}(w)$ of the result, we then use the free additive convolution property in order to 
	find the R-transform of the entire equivalent channel $\tilde{R}_{D}(w)$. 
\item
	Using property \eqref{ST_property}, we can find the the R-transform of the 
	covariance matrix of the symmetrized channel, $\tilde{R}_{DD^H}(w)$ . We can then find $\tilde{G}_{DD^H}(s)$ and 
	use the inversion to find the symmetrized AED.

@@

\subsection{Solving for $G_{D_kD_k^H}(s)$}\label{Polynomial_terms}
For the model presented we have 
\begin{equation}
D_k = G_B \boldsymbol{\Theta}_N H_N \cdots \boldsymbol{\Theta}_1 H_1
\end{equation}
and 
\begin{equation}
C_N = D_kD_k^H = [G_B \boldsymbol{\Theta}_N H_N \cdots \boldsymbol{\Theta}_1 H_1]
[H_1 \boldsymbol{\Theta}_1 \cdots H_N \boldsymbol{\Theta}_N G_B]
\end{equation}
\begin{itemize}
\item 
	Because commuting matrix multiplication does not change the non-zero eigen value distribution, we consider 
	the matrix 
\begin{equation}
\tilde{C}_N = [\boldsymbol{\Theta}_1^H \cdots H_N^H \boldsymbol{\Theta}_N^H G_B^H][G_B \boldsymbol{\Theta}_N  \cdots \boldsymbol{\Theta}_1 H_1 H_1^H]
\end{equation}

\item 
	We use the rotational property of the Stieltjes transform and S-Transform. 
\begin{equation}
S_{C_N}(z) = \frac{z+1}{z+\chi_N} S_{\tilde{C}_N}(\frac{z}{\chi_N})
\end{equation}
